RCloud: DevOps for Visual Analysis and Data Science

### 2014-03-18 discussion.tex
yes

% limitations
Previous studies have pointed out difficulties in achieving the flexibility,
scalability and maintainability expected of production software with experimental
code created by data analysts.
Although these properties cannot be enforced by any programming environment,
suitable tools can help well-motivated analysts and programmers to create
robust applications with much less effort.

@@

>>>>

% limitations
Previous studies have pointed out difficulties in achieving the flexibility,
scalability and maintainability expected of production software in experimental
code written by data analysts.
Although these properties cannot be enforced by any programming environment,
suitable tools can help well-motivated analysts and programmers to create
robust applications with much less effort.

@@

Had to back off only one language sooner than we expected.

Shared artifacts, artifact histories, 
Discussion
View sharing - bookmarking, everything available as a URL
Content export - want to avoid, create ways of working where this is not necessary.
Social-psychological incentives - starring
Voting and ranking - starring

Group management, size, diversity.  Lacking support,but clearly desirable.

Has to play well in the ecosystem of the other tools and worked out as planned but there is a temptation to absorb

What is relationship to a standard CMS with R/Python
